Moral Foundations of U.S. Political News Organizations

### 2019-03-25 pilot_manuscript.Rmd
stuff
here's the powerpoint

```{r create_datasets_ingroup, include=FALSE}
ingroup_all = read.csv("iexp1_data/ngroup_words_total.csv", stringsAsFactors = F)

@@

```{r exp1 source descriptives, results = 'asis', echo = FALSE}
#Get the final dataset split into the 4 sources
final$Source = as.factor(final$Source)
NYtimesDesc1 = subset(final, Source == "NY Times") #number of obs. = number of articles for that source; NYT = 406
NPRDesc1 = subset(final, Source == "NPR") #NPR = 695 articles
FoxDesc1 = subset(final, Source == "Fox News") #Fox = 503 articles
BreitbartDesc1 = subset(final, Source == "Breitbart") #Breitbart = 1,437 articles

@@

for (i in 49:length(urlslist3)){

@@

#loop over the results and go through them
##18 pages
for (i in 1:47){

>>>>

```{r create_datasets_ingroup, include=FALSE}
ingroup_all = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)

@@

```{r exp1 source descriptives, results = 'asis', echo = FALSE}

final$uniquewords = NA
final$valenceavg = NA

for (i in 1:nrow(final)){

  #add unique
  final$uniquewords[i] = length(unique(unlist(strsplit(final$stemmed[i], " "))))

  #add valence
  tempwords = as.data.frame(unlist(strsplit(final$stemmed[i], " ")))
  colnames(tempwords) = "theword"
  tempwords$tempval = vlookup(tempwords$theword, #index in original data
                    warriner, #where's the stuff you want to put in
                    "V.Mean.Sum", #what column is the stuff you want
                    "Word2") #what's the matching index

#Get the final dataset split into the 4 sources
final$Source = as.factor(final$Source)
NYtimesDesc1 = subset(final, Source == "NY Times") #number of obs. = number of articles for that source; NYT = 406
NPRDesc1 = subset(final, Source == "NPR") #NPR = 695 articles
FoxDesc1 = subset(final, Source == "Fox News") #Fox = 503 articles
BreitbartDesc1 = subset(final, Source == "Breitbart") #Breitbart = 1,437 articles

@@

@@

#loop over the results and go through them
##47 pages
for (i in 1:47){
